%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvpubs}
    \cvpub{\textit{Long QT Syndrome: Beyond Beta Blockers}. \textbf{East of England ICC Training Day}. 2026. Newmarket, UK.}

    \cvpub{\textit{Risk stratification in Brugada Syndrome: a case presentation}. \textbf{British Cardiac Society}. 2025. Manchester, UK.}

    \cvpub{\textit{The Devil is in the Detail: nodofascicular VT}. \textbf{British Heart Rhythm Society}. 2025. Edinburgh, UK.}

    \cvpub{\textit{What you’re missing matters: integrating short and long-read scRNA-seq}. \textbf{Oxford Nanopore Symposium}. 2024. Oxford, UK.}

    \cvpub{\textit{Spatial Transcriptomics in Human Cell Atlasing}. \textbf{SpatialBiology 2023}. 2023. Online.}

    \cvpub{\textit{Gene regulatory networks underlying cardiogenesis}. \textbf{European Society of Cardiology Congress}. 2023. Amsterdam, NL.}

    \cvpub{\textit{A spatially-resolved multiomic atlas of human cardiac development}. \textbf{HCA General Meeting}. 2023. Toronto, CA.}

    \cvpub{\textit{The adult and developing heart, one cell at a time}. \textbf{The Royal Society}. 2023. London, UK.}

    \cvpub{\textit{The Hopes and Fears Lab (Public Engagement event)}. \textbf{Cambridge Alumni Festival}. 2022. Cambridge, UK.}

    \cvpub{\textit{Single-cell atlasing of the heart}. \textbf{BHF Symposium}. 2022. Online.}

    \cvpub{\textit{A novel variant causing JLNS, but not LQT1}. \textbf{Heart Rhythm Congress}. 2019. Birmingham, UK.}

    \cvpub{\textit{Effusive-constrictive pericarditis – a complication of PCI}. \textbf{British Society of Cardiac Imaging}. 2019. Cambridge, UK.}

    \cvpub{\textit{Haematoma risk post-angiography}. \textbf{Society for Cardiac Interventions \& Angiography (SCAI)}. 2014. San Diego, USA.}
\end{cvpubs}