%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{center}
H-index 13 | Total citations 1,471 | ORCID \href{https://orcid.org/0000-0002-0408-5801}{0000-0002-0408-5801}
\end{center}

\vspace{0.5em}

\begin{center}
Full publication list available via \href{https://scholar.google.co.uk/citations?hl=en&user=3bPMK_oAAAAJ}{Google Scholar}
\end{center}

% %---------------------------------------------------------
\cvsubsection{Co-First Author}
% %---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Cranley J*}, Mach L*, Jimba T, Kanemaru K, Zhao J, Perera S, Zurke Y-X, Koplev S, Barnett S, Wang L, Roberts K, Kapuge R, Richardson L, Polanski K, Semprich C, Ho SY, Robertus JL, Madrova M, Tegshjargal B, Miranda AMA, Sarropoulos I, Cujba A-M, Lee W, Wilbrey-Clark A, Palmer J, Brunet J, Prasad S, Chowdhury R, Dark J, Lee P, Jørgensen H, Noseda M\#, Teichmann SA\#. 2026. Multimodal Hypersampling of the adult human heart resolves tissue-specific cell states and disease-associated variants. Under review at \textit{Nature}.}

    \cvpub{\textbf{Cranley J*}, Kanemaru K*, Bayraktar S*, Knight-Schrijver V, Hulbert R, Lana-Elola E, Aoidi R, Pett JP, Wilbrey-Clark A, Polanski K, Dabrowska M, Mulas I, Johnson H, Richardson L, Semprich CI, Kapuge R, Perera S, He X, Ho SY, Yayon N, Tuck L, Roberts K, Palmer JA, Davaapil H, Gambardella L, Patel M, Tyser R, Bernardo AS, Tybulewicz VLJ, Sinha S, Teichmann SA. 2024. Developmental Dynamics of Human Cardiogenesis: A multi-omic reference and its disruption in Trisomy 21. \href{https://doi.org/10.1101/2024.04.29.591736}{DOI} Under review at \textit{Nature}.}

    \cvpub{Bayraktar S*, \textbf{Cranley J*}, Kanemaru K*, Knight-Schrijver V, Colzani M, Davaapil H, Lee JCM, Polanski K, Richardson L, Semprich CI, Kapuge R, Dabrowska M, Mulas I, Perera S, Patel M, Ho SY, He X, Tyser R, Gambardella L, Teichmann SA, Sinha S. 2024. High-resolution atlas of the developing human heart and the great vessels. \href{https://doi.org/10.1101/2024.04.27.591127}{DOI} Under review at \textit{Nature Cardiovascular Research}.}

    \cvpub{Kanemaru K*, \textbf{Cranley J*}, Muraro D, Miranda AMA, Ho SY, Wilbrey-Clark A, Patrick Pett J, Polanski K, Richardson L, Litvinukova M, Kumasaka N, Qin Y, Jablonska Z, Semprich CI, Mach L, Dabrowska M, Richoz N, Bolt L, Mamanova L, Kapuge R, Barnett SN, Perera S, Talavera-López C, Mulas I, Mahbubani KT, Tuck L, Wang L, Huang MM, Prete M, Pritchard S, Dark J, Saeb-Parsy K, Patel M, Clatworthy MR, Hübner N, Chowdhury RA, Noseda M, Teichmann SA. 2023. Spatially resolved multiomics of human cardiac niches. \textit{Nature}, 619(7971): 801–810. \href{https://doi.org/10.1038/s41586-023-06311-1}{DOI}}
    
\end{cvpubs}

%---------------------------------------------------------
\clearpage
\cvsubsection{Collaborative}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{Pett JP, Prete M, Pham D, England N, Yuan H, Prigmore E, Tuck L, Oszlanczi A, To K, Xu C, Suo C, Dann E, He P, Kedlian V, Kanemaru K, \textbf{Cranley J}, Yang L, Elmentaite R, Oliver AJ, Cujba AM, Cakir B, Murray S, Mahbubani KT, Saeb-Parsy K, Gambardella L, Kasper M, Haniffa M, Nawijn MC, Teichmann SA, Meyer KB. 2025. An atlas of TF driven gene programs across human cells. \href{https://doi.org/10.1101/2025.05.30.657075}{DOI}}

    \cvpub{Troulé K*, Petryszak R, Cakir B, \textbf{Cranley J}, Harasty A, Prete M, Tuong ZK, Teichmann SA, Garcia-Alonso L, Vento-Tormo R. 2025. CellPhoneDB v5: inferring cell–cell communication from single-cell multiomics data. \textit{Nature Protocols}. \href{https://doi.org/10.1038/s41596-024-01137-1}{DOI}}
    
    \cvpub{Nicastro M*, Vermeer AM, Postema PG, Tadros R, Bowling FZ, Aegisdottir HM, Tragante V, Mach L, Postma AV, Lodder EM, van Duijvenboden K, Zwart R, Beekman L, Wu L, Jurgens SJ, van der Zwaag PA, Alders M, Allouba M, Aguib Y, Santome JL, de Una D, Monserrat L, Miranda AM, Kanemaru K, \textbf{Cranley J}, van Zeggeren IE, Aronica EM, Ripolone M, Zanotti S, Sveinbjornsson G, Ivarsdottir EV, Hólm H, Guðbjartsson DF, Skúladóttir ÁT, Stefánsson K, Nadauld L, Knowlton KU, Ostrowski SR, Sørensen E, Vesterager Pedersen OB, Ghouse J, Rand SA, Bundgaard H, Ullum H, Erikstrup C, Aagaard B, Bruun MT, Christiansen M, Jensen HK, Carere DA, Cummings CT, Fishler K, Tørring PM, Brusgaard K, Juul TM, Saaby L, Winkel BG, Mogensen J, Fortunato F, Comi GP, Ronchi D, van Tintelen JP, Noseda M, Airola MV, Christiaans I, Wilde AA, Wilders R, Clur SA, Verkerk AO, Bezzina CR, Lahrouchi N. 2025. Bi-allelic variants in POPDC2 cause an autosomal recessive syndrome presenting with cardiac conduction defects and hypertrophic cardiomyopathy. \textit{The American Journal of Human Genetics}, 112(7): 1681–1698. \href{https://doi.org/10.1016/j.ajhg.2025.04.016}{DOI}}

    \cvpub{To K*, Fei L*, Pett JP, Roberts K, Blain R, Polański K, Li T, Yayon N, He P, Xu C, \textbf{Cranley J}, Moy M, Li R, Kanemaru K, Huang N, Megas S, Richardson L, Kapuge R, Perera S, Tuck E, Wilbrey-Clark A, Mulas I, Memi F, Cakir B, Predeus AV, Horsfall D, Murray S, Prete M, Mazin P, He X, Meyer KB, Haniffa M, Barker RA, Bayraktar O, Chédotal A, Buckley CD, Teichmann SA. 2024. A multi-omic atlas of human embryonic skeletal development. \textit{Nature}, 635(8039): 657–667. \href{https://doi.org/10.1038/s41586-024-08189-z}{DOI}}

    \cvpub{Barnett SN*, Cujba AM*, Yang L*, Maceiras AR, Li S, Kedlian VR, Pett JP, Polanski K, Miranda AMA, Xu C, \textbf{Cranley J}, Kanemaru K, Lee M, Mach L, Perera S, Tudor C, Joseph PD, Pritchard S, Toscano-Rivalta R, Tuong ZK, Bolt L, Petryszak R, Prete M, Cakir B, Huseynov A, Sarropoulos I, Chowdhury RA, Elmentaite R, Madissoon E, Oliver AJ, Campos L, Brazovskaja A, Gomes T, Treutlein B, Kim CN, Nowakowski TJ, Meyer KB, Randi AM, Noseda M, Teichmann SA. 2024. An organotypic atlas of human vascular cells. \textit{Nature Medicine}, 30(12): 3468–3481. \href{https://doi.org/10.1038/s41591-024-03376-x}{DOI}}

    \cvpub{Brunet J, Cook AC, Walsh CL, \textbf{Cranley J*}, Tafforeau P, Engel K, Arthurs O, Berruyer C, Burke O’Leary E, Bellier A, Torii R, Werlein C, Jonigk DD, Ackermann M, Dollman K, Lee PD. 2024. Multidimensional Analysis of the Adult Human Heart in Health and Disease Using Hierarchical Phase-Contrast Tomography. \textit{Radiology}, 312(1). \href{https://doi.org/10.1148/radiol.232731}{DOI}}

    \cvpub{Knight-Schrijver VR*, Davaapil H, Bayraktar S, Ross ADB, Kanemaru K, \textbf{Cranley J}, Dabrowska M, Patel M, Polanski K, He X, Vallier L, Teichmann S, Gambardella L, Sinha S. 2022. A single-cell comparison of adult and fetal human epicardium defines the age-associated changes in epicardial activity. \textit{Nature Cardiovascular Research}. \href{https://doi.org/10.1038/s44161-022-00183-w}{DOI}}

    \cvpub{Reichart D*, Lindberg EL*, Maatz H, Miranda AMA, Viveiros A, Shvetsov N, Gärtner A, Nadelmann ER, Lee M, Kanemaru K, Ruiz-Orera J, Strohmenger V, DeLaughter DM, Patone G, Zhang H, Woehler A, Lippert C, Kim Y, Adami E, Gorham JM, Barnett SN, Brown K, Buchan RJ, Chowdhury RA, Constantinou C, \textbf{Cranley J}, Felkin LE, Fox H, Ghauri A, Gummert J, Kanda M, Li R, Mach L, McDonough B, Samari S, Shahriaran F, Yapp C, Stanasiuk C, Theotokis PI, Theis FJ, Bogaerdt AVD, Wakimoto H, Ware JS, Worth CL, Barton PJR, Lee YA, Teichmann SA, Milting H, Noseda M, Oudit GY, Heinig M, Seidman JG, Hubner N, Seidman CE. 2022. Pathogenic variants damage cell composition and single cell transcription in cardiomyopathies. \textit{Science}, 377(6606). \href{https://doi.org/10.1126/science.abo1984}{DOI}}

    \cvpub{Miranda AMA*, Janbandhu V, Maatz H, Kanemaru K, \textbf{Cranley J}, Teichmann SA, Hübner N, Schneider MD, Harvey RP, Noseda M. 2022. Single-cell transcriptomics for the assessment of cardiac disease. \textit{Nature Reviews Cardiology}. \href{https://doi.org/10.1038/s41569-022-00805-7}{DOI}}

    \cvpub{Ntalla I*, Weng LC, Cartwright JH, Hall AW, Sveinbjornsson G, Tucker NR, Choi SH, Chaffin MD, Roselli C, Barnes MR, Mifsud B, Warren HR, Hayward C, Marten J, \textbf{Cranley J}, Concas MP, Gasparini P, Boutin T, Kolcic I, Polasek O, Rudan I, Araujo NM, Lima-Costa MF, Ribeiro ALP, Souza RP, Tarazona-Santos E, Giedraitis V, Ingelsson E, Mahajan A, Morris AP, Del Greco M F, Foco L, Gögele M, Hicks AA, Cook JP, Lind L, Lindgren CM, Sundström J, Nelson CP, Riaz MB, Samani NJ, Sinagra G, Ulivi S, Kähönen M, Mishra PP, Mononen N, Nikus K, Caulfield MJ, Dominiczak A, Padmanabhan S, Montasser ME, O’Connell JR, Ryan K, Shuldiner AR, Aeschbacher S, Conen D, Risch L, Thériault S, Hutri-Kähönen N, Lehtimäki T, Lyytikäinen LP, Raitakari OT, Barnes CLK, Campbell H, Joshi PK, Wilson JF, Isaacs A, Kors JA, van Duijn CM, Huang PL, Gudnason V, Harris TB, Launer LJ, Smith AV, Bottinger EP, Loos RJF, Nadkarni GN, Preuss MH, Correa A, Mei H, Wilson J, Meitinger T, Müller-Nurasyid M, Peters A, Waldenberger M, Mangino M, Spector TD, Rienstra M, van de Vegte YJ, van der Harst P, Verweij N, Kääb S, Schramm K, Sinner MF, Strauch K, Cutler MJ, Fatkin D, London B, Olesen M, Roden DM, Benjamin Shoemaker M, Gustav Smith J, Biggs ML, Bis JC, Brody JA, Psaty BM, Rice K, Sotoodehnia N, De Grandi A, Fuchsberger C, Pattaro C, Pramstaller PP, Ford I, Wouter Jukema J, Macfarlane PW, Trompet S, Dörr M, Felix SB, Völker U, Weiss S, Havulinna AS, Jula A, Sääksjärvi K, Salomaa V, Guo X, Heckbert SR, Lin HJ, Rotter JI, Taylor KD, Yao J, de Mutsert R, Maan AC, Mook-Kanamori DO, Noordam R, Cucca F, Ding J, Lakatta EG, Qian Y, Tarasov KV, Levy D, Lin H, Newton-Cheh CH, Lunetta KL, Murray AD, Porteous DJ, Smith BH, Stricker BH, Uitterlinden A, van den Berg ME, Haessler J, Jackson RD, Kooperberg C, Peters U, Reiner AP, Whitsel EA, Alonso A, Arking DE, Boerwinkle E, Ehret GB, Soliman EZ, Avery CL, Gogarten SM, Kerr KF, Laurie CC, Seyerle AA, Stilp A, Assa S, Abdullah Said M, Yldau van der Ende M, Lambiase PD, Orini M, Ramirez J, Van Duijvenboden S, Arnar DO, Gudbjartsson DF, Holm H, Sulem P, Thorleifsson G, Thorolfsdottir RB, Thorsteinsdottir U, Benjamin EJ, Tinker A, Stefansson K, Ellinor PT, Jamshidi Y, Lubitz SA, Munroe PB. 2020. Multi-ancestry GWAS of the electrocardiographic PR interval identifies 202 loci underlying cardiac conduction. \textit{Nature Communications}, 11(1). \href{https://doi.org/10.1038/s41467-020-15706-x}{DOI}}

\clearpage
\cvsubsection{Earlier Work}

    \cvpub{\textbf{Cranley J*}, MacRae CA. 2018. A New Approach to an Old Problem: One Brave Idea. \textit{Circulation Research}, 122(9): 1172–1175. \href{https://doi.org/10.1161/circresaha.118.310941}{DOI}}

    \cvpub{Herring N*, \textbf{Cranley J}, Lokale MN, Li D, Shanks J, Alston EN, Girard BM, Carter E, Parsons RL, Habecker BA, Paterson DJ. 2012. The cardiac sympathetic co-transmitter galanin reduces acetylcholine release and vagal bradycardia: Implications for neural control of cardiac excitability. \textit{Journal of Molecular and Cellular Cardiology}, 52(3): 667–676. \href{https://doi.org/10.1016/j.yjmcc.2011.11.016}{DOI}}
    
\end{cvpubs}
