\cvsection{Research Experience}

\begin{cventries}

\textbf{Post-doctoral (NIHR Academic Clinical Lectureship)}  
\cventry
  {Supervisor: Prof. Sarah Teichmann}
  {University of Cambridge}
  {Cambridge, UK}
  {2024–present}
  {
    \begin{cvitems}
      \item {Establishing an integrated framework linking single-cell resolved cardiac function with genomic variation, bridging electrophysiology and multiomic datasets to uncover arrhythmia mechanisms.}
      \item {Building collaborations across computational and experimental groups to translate cell atlases into mechanistic insight.}
      \item {Supervision of Masters and PhD students in the Teichmann Lab. Leading the Heart team subgroup meetings.}
    \end{cvitems}
  }

\newpage
\textbf{Doctorate (Wellcome Trust PhD in Genomics)}  
\cventry
  {Supervisor: Prof. Sarah Teichmann}
  {Sanger Institute}
  {Hinxton, UK}
  {2020–2024}
  {
    \begin{cvitems}
      \item {Developed single-cell and spatial multiomic maps of the adult and foetal human heart, defining transcriptional and spatial cell states underlying cardiac development and disease.}
      \item {Work led to first-author papers in \textit{Nature} (2023) and collaborative outputs in \textit{Nature Cardiovascular Research} and \textit{Science}.}
    \end{cvitems}
  }

\textbf{Pre-doctoral (NIHR Academic Clinical Fellowship)}  
\cventry
  {Supervisor: Prof. Patsy Munroe}
  {Queen Mary University of London}
  {London, UK}
  {2017}
  {
    \begin{cvitems}
      \item {Performed genome-wide association analyses identifying modulators of the PR interval, contributing to multi-ancestry meta-analyses of cardiac conduction phenotypes.}
    \end{cvitems}
  }

\cventry
  {Supervisor: Prof. Calum MacRae}
  {Harvard University}
  {Boston, MA, USA}
  {2016}
  {
    \begin{cvitems}
      \item {Investigated non-canonical genomic and phenotypic predictors of coronary artery disease within translational cardiovascular genomics programmes.}
    \end{cvitems}
  }

\cventry
  {Supervisor: Prof. Chris Huang}
  {University of Cambridge}
  {Cambridge, UK}
  {2015}
  {
    \begin{cvitems}
      \item {Applied whole-cell patch clamping to study the impact of \textit{Pgc1}\textsuperscript{β} deficiency on cardiac sodium current kinetics, linking bioenergetic dysfunction with arrhythmogenic substrates.}
    \end{cvitems}
  }

\textbf{Undergraduate (Intercalated BSc, Physiology)}  
\cventry
  {Supervisors: Prof. Neil Herring, Prof. David Paterson}
  {University of Oxford}
  {Oxford, UK}
  {2011}
  {
    \begin{cvitems}
      \item {Explored the role of galanin in cardiac autonomic regulation, identifying neuromodulatory effects on vagal tone (published in \textit{J Mol Cell Cardiol}, 2012).}
    \end{cvitems}
  }

\end{cventries}