%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Management, Leadership \& Responsibilities}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\cvsubsection{Management}

\begin{cvpubs}
    \cvpub{\textbf{Clinical Research, Education \& Leadership (CREL) module}. Completed the one-year part-time module hosted by the University of Cambridge, covering clinical management and leadership specifically designed for healthcare professionals within the NHS context.}

    \cvpub{\textbf{Medical Director's Office Fellowship}. Completed a 12-month fellowship in the Medical Director’s Office at Royal Papworth Hospital, gaining insight into clinical governance, leadership, and quality improvement. Led a project to improve equity in registrar training opportunities.}

    \cvpub{\textbf{Cardiology rota manager}. In this 12 month post I was responsible for constructing the termly and weekly rotas and liaison with the consultant body. During this role I gained experience of personnel management, navigated 2 strikes, filled a large rota gap, and successful proposed a business case and created a job advert for a clinical fellow.}

    \cvpub{\textbf{BJCA representative to the BHRS}. I represented the BJCA interest (electrophysiology and devices trainees) at BHRS committee meetings. I also attended BJCA committee meetings.}

    \cvpub{\textbf{East of England trainee representative (Digital \& Training Days)}. I constructed a website for cardiology trainees as well as organising regional training events.}
    
\end{cvpubs}

%\cvsubsection{Peer Review}

%\begin{small} \color{black}  
%FOO BAR
%\end{small}

%\cvsubsection{Professional Memberships}

%\begin{small} \color{black}
%One fancy society \\
%Another fancy society \\
%\end{small}